GSEA datasets for FDR benchmarking

### 2017-12-08 datasets/GSEA/gsea.Rmd
local changes

```{r plottingResults}
rejections_scatter( sGSEA, as_fraction=TRUE, supplementary=FALSE)

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)
rejection_scatter_bins( sGSEA, "ind_covariate", threshold=15, bins=4, as_fraction=TRUE, supplementary=FALSE)
```

@@

table( set1 )
table( set2 )

@@

```{r, eval=FALSE }
nms <- names( genes )
xx <- seq_len(length(nms))
gns <- 1*( xx %in% sample( xx, 1000, replace=FALSE ) )
names( gns ) <- nms
pwf <- nullp( gns, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )
res <- goRes %>%
  dplyr:::filter( numDEInCat > 0 ) %>%
  dplyr:::select( c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
pr <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(pr) <- "qvalue"
pr <- addDefaultMetrics(pr)

>>>>

```{r plottingResults}
rejections_scatter( sGSEA, as_fraction=FALSE, supplementary=FALSE)

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)

estimatePerformanceMetrics( sGSEA, alpha=0.1, tidy=TRUE ) %>%
  filter( blabel %in% c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf") ) %>%
  select( blabel, value )

rejection_scatter_bins( sGSEA, "ind_covariate", threshold=15, bins=4, as_fraction=FALSE, supplementary=FALSE)
```

@@

sizesDf <- data.frame( 
  size=c( rowData( sGSEA )$ind_covariate[which(set1)], 
          rowData( sGSEA )$ind_covariate[which(set2)], 
          rowData( sGSEA )$ind_covariate[which(set3)] ),
  label=rep(c("set1", "set2", "set3"), c(sum(set1), sum(set2), sum(set3)) ) )

ggplot( sizesDf, aes( label, log2(size) )) +
  geom_boxplot()

dim(goRes)

goRes[set1,]

@@

```{r, eval=FALSE }

nms <- names( genes )
xx <- seq_len(length(nms))
gns <- 1*( xx %in% sample( xx, 1000, replace=FALSE ) )
names( gns ) <- nms
pwf <- nullp( gns, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )
res <- goRes %>%
  dplyr:::filter( numDEInCat > 0 ) %>%
  dplyr:::select( c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
pr <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(pr) <- "qvalue"
pr <- addDefaultMetrics(pr, metrics="rejections")

estimatePerformanceMetrics( pr, alpha=0.1, tidy=TRUE ) %>%
  filter( blabel %in% c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf") ) %>%
  select( blabel, value )
